Figures and tables for paper

### 2021-10-06 analysis/04_figs-tables.Rmd
More hypotheses answers using market simulator.

@@

@@

@@

contrasts <- tibble(
  financial_transparency = draws %>% filter(level == "Handful of wealthy private donors") %>% select(Gamma) %>% pull(),
  accountibility = draws %>% filter(level == "Government grants") %>% select(Gamma) %>% pull()
  )

@@

@@

## Model fit table

>>>>

Market share when criticized:
A = 0.130767214
G = 0.212870677
O = 0.218368082
R = 0.437994028

Market share under crackdown:
A = 0.130767214
G = 0.212870677
O = 0.218368082
R = 0.437994028

Tentative yes, O and R claim greater market share compared to A and G

@@

Market shares:

ER = 0.318332453
EV = 0.203877752
HR = 0.159886134
RR = 0.31790366

ER>RR>EV>HR, evidence that hypothesis is correct

@@

Market shares:

numerous donors/not under crackdown = 0.247967551
numerous donors/under crackdown = 0.271016037
few donors/under crackdown = 0.26213647
government grants/under crackdown = 0.218879942

Though numerous donors/under crackdown has the largest market share, the difference between them is almost insignificant. Personally, this evidence doesn't seem convincing.

@@

contrasts <- tibble(
  financial_transparency = draws %>% filter(level == "Financial transparency") %>% select(Gamma) %>% pull(),
  accountability = draws %>% filter(level == "Accountability") %>% select(Gamma) %>% pull()
  )

# Plot the contrasts
contrasts %>%
  pivot_longer(financial_transparency:accountability, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

# Save plot
ggsave(
  "contrasts_hypothesis05.png",
  path = here::here("analysis", "output", "figures"),
  width = 12,
  height = 6,
  units = "in"
)

@@

Expected utility (Transparency/Few donors/Under crackdown):

(1/0/1)	= 3.346877215
(1/1/1)* =	3.237220167
(1/1/0)	= 2.961911648
(0/1/1)	= 2.174492071
(0/0/1)	= 2.248150447
(0/0/0)	= 2.056957096
(1/0/0)	= 3.062242941

Market shares: 
(1/0/1)	= 0.175340698
(1/1/1)* =	0.169595837
(1/1/0)	= 0.155172605
(0/1/1)	= 0.113920211
(0/0/1)	= 0.117779124
(0/0/0)	= 0.10776263
(1/0/0)	= 0.160428895

Not sure if this is the best way to do triple interaction, but I gave it a shot. I included expected utility as well as market share, as market share may understate the difference in willingness to donate (market share is split between 7 orgs instead of 4).

NGOs that are financially transparent, are supported by few donors, and are under crackdown receive the second largest share of the market--they are topped by firms which are transparent and under crackdown, but are supported by numerous donors. This would contradict the hypothesis, assuming I did this correctly.

@@

Market share:

Accountability = 0.566631341
No Accountability = 0.433368659

The difference is large enough to suggest that accountability increases donors likelihood to donate, contrary to the hypothesis.
## Model fit table
